% question two
\question{2}{0.9 points}

\note{Estimate a multivariate regression model explaining income as a function of BMI and whether the individual is black. Thus, estimate: \begin{equation*}\text{Income}= \beta_0 + \beta_1\text{BMI} + \beta_2\text{Black} + u\end{equation*}}

\vspace{-1em}

Using \icode{reg} with robust SE estimators:

\begin{minted}{stata}
reg income bmi black, robust
\end{minted}

\begin{table}[H]
    \begin{center}
        \caption{Linear regression}
        \input{\tables reg2.tex}
        \label{tab:reg2}    
    \end{center}
\end{table}

\subquestion{a}{Interpret the estimated coefficients of all the explanatory variables (\textbf{sign, magnitude, and significance}).}

For the explanatory variable \icode{bmi}, the negative coefficient implies a negative relationship. The magnitude of the coefficient, 307.3532, implies that for each unit increase in BMI, an individual's observed annual income would decrease by roughly 307\$, ceteris paribus. Finally, it can be determined that the \icode{bmi} variable is not significant, as its p-value (0.269) exceeds our significance level (0.05).

In the case of the variable \icode{black}, the negative coefficient implies an also negative relationship with the dependent variable. The magnitude of the coefficient, 4839.756, implies a decrease of roughly 4840\$ \space in observed annual income if an individual belongs to the black ethnic group, ceteris paribus. As in the case of \icode{bmi}, \icode{black}'s p-value (0.344) exceeds the significance level, meaning it is not significant.

\subquestion{b}{What is the estimated 95\% Confidence Interval of $\beta_1$? What can you conclude based on the information in this confidence interval about the \textbf{effect of BMI on income}?}

As seen in the regression above, the estimated 95\% CI of $\beta_1$ is [-788.01, 286.60]. Since 0 falls within it, we cannot reject the null hypothesis that BMI has no effect on income at the 5\% significance level. This aligns with the conclusions derived from analyzing the p-values in the previous question.

\subquestion{c}{What is the \textbf{relative magnitude} of the effect of being black on income? Interpret the relative magnitude.}

The relative magnitude of being black on income can be explained as the \% change in income experienced if an individual belongs to the black ethnic group, everything else notwithstanding. We can calculate it as:

\vspace{-1em}

\begin{equation}
    \text{Relative Magnitude} = \frac{-4,839.75}{41,514.35} = -0.117 \text{ (11.7\%)}
\end{equation}

We can therefore determine that the coefficient for black ethnicity represents roughly 11.65\% of mean annual income.